\section{Acknowledgements}

This thesis is the culmination of nearly six years 
of scrambling to acquire and apply new knowledge and ideas,
and it includes work performed and discussed across several continents. 
I am deeply indebted to many people for enabling me to accomplish this
successfully and for tolerating the challenges that it has brought.
First and foremost, I am grateful
to my wonderful wife, Emily. You have showed boundless
personal strength and independence while being a constant pillar of 
support for me. I cannot thank you enough.

Thank you to my parents for teaching me to value knowledge,
encouraging me to pursue my interests, and supporting me throughout. Thank
you to my siblings for always setting a good example and for remaining 
my closest friends as we grow older.
Thank you also to my in laws for welcoming me into their family with love and support.
My grandfather, Kenneth Buchanan, deserves a special mention. 
The fact that you watched a series a lectures on quantum mechanics, 
and read this work from cover to cover, is a testament to both your support
and deep commitment to the pursuit of knowledge.

My advisor, Professor Matt Herndon, has guided me through all of the work discussed
in this thesis and more.
You are a great physicist, a thoughtful and attentive supervisor,
and a genuine and caring person. Thank you for directing me towards interesting
projects, giving me guidance and attentive support, and for 
granting me the independence to pursue my own ideas and interests.
The Wisconsin CMS group is a wonderfully collaborative environment,
and I was lucky to also benefit from the deep knowledge and professional examples
of Professors Sridhara Dasu, Wesley Smith, Tulika Bose, and Kevin Black. 
I was privileged to work with Wesley up until his recent retirement;
your steadfast commitment to work that is both rigorously
supported and carefully communicated has been a wonderful example.

The students, postdocs, and scientists I worked with at UW were an invaluable 
source of knowledge and entertainment. 
Thank you especially to Senka Duric, who was always supportive and
encouraging, and to 
Sascha Savin for providing a ceaseless example of scientific
rigor and passion.  
Thank you to all the current and former students with whom I have worked.
Nick Smith and Tyler Ruggles came to Wisconsin with me, 
helped me through classes (including French), and moved to Geneva
alongside me. Aaron Levine, Tom Perry, Laura Dodd, Nate Woods, Devin Taylor,
and Usama Hussain, and James Buchanan have all played a part in helping my
scientific work advance and in keeping me sane. The fact that you can all
still be summoned on Skype says a lot about the camaraderie of our group.

The CMS Collaboration is built from the work of thousands of physicists,
without whom this thesis would not be possible. Thank you to
my collaborators at MIT, Princeton, and Fermilab for pushing the quality
and scope of this work forward.
I am indebted to the CMS generators and Standard Model groups 
for cultivating receptive environments that place scientific merit above
seniority and established conventions.
Thank you also to the members of the CMS CSC group, particularly those
who helped me navigate the terrors of being the first line of defense
against problems with data collection in the middle of the night.

Lastly, thank you to all my friends in Madison, Geneva,
and everywhere else,
who provided a welcome respite from the pressures and challenges of
research, teaching, and classes. From my fellow classmates, to my friends from cycling and
the CERN Football Club, I have met wonderful people who stand out
as much for their generosity and caring as for their incredible talents
and intellect. I would like to thank you all by name, but I would
risk leaving someone out.
