\chapter{Vector boson scattering in the standard model and beyond}
\label{ch:phenomenology}

The known particle content of the universe and the forces through which
they interact were introduced in the previous Chapter. To the best of our
current knowledge, all collisions at the LHC involve only these objects
\section{The Standard Model}
Overview of the particle contact, the forces and the gauge fields

Write down a more formal theory of the standard model.

Write down the SM Legrangian. Mention the SU(3)xSU(2)xU(1) structure 
of the SM. 
\section{Electroweak symmetry breaking}
\section{Multi-boson production and interactions}
\section{Probing the electroweak sector through vector boson scattering}
\section{New interactions in vector boson scattering}

Emboldened by the prospects of new physics in modifying \WZjj production
at the LHC, 

Introduction to the 


\subsection{Additional Higgs bosons and the Georgi-Machacek model}

In the SM, EWSB is realized by a single isospin doublet scalar field.
This field is sufficient to give mass to the $\PW$ and $\cPZ$
bosons, while resulting in the scalar $\PH$ boson, consistent with the observed
boson with $m_{\PH} = 125\GeV$.  Especially given the complexity of the fermion sector
of the SM, it is natural to ask if the universe contains a more complex
structure of scalar fields than the single doublet. 
However, SM extensions by arbitrary \SUtwo scalar fields 
are high constrained by the parameter $\rho \equiv m_\PW^2/m_\PZ^w\cos^2\theta$,
experimentally established to be very close to 1~\cite{}.
For a theory with $n$ scalar multiplets
$\phi_i$, with weak Isospin $I_i$, weak hypercharge $Y_i$, and vacuum expectation
value $v_i$, $\rho$ is given defined in terms of the quantum numbers of the fields
by the following expression at tree level~\cite{Branco:2011iw}
\begin{equation}
  \rho = \sum_{i = 1}^{n} \frac{I_i(I_i+1) - \frac{1}{4}Y_i^2}
              {\frac{1}{2}Y_i^2 v_i} \,,
  \labe{eq:rho}
\end{equation}
Extending the scalar sector of the SM by two rather than one doublet satisfies
this expression. This model, known as the Two-Higgs-doublet model (2HDM), has
been extensively studied, in part because the scalar sector of SUSY has this form.
The 2HDM gives rise to a heavy Higgs boson, a pseudoscalar Higgs boson, and 
charged Higgs bosons $\PH^{\pm}$ in addition to a light SM-like Higgs boson.
In this model, the $\PH^{\pm}$ bosons coupling strongly to the leptons,
and decays to bosons are strongly suppressed in the mass range probed by the LHC~\cite{Arhrib:2016wpw}.

An alternative extension of the Higgs sector of the SM that satisfies experimental
constraints on $\rho$ was first proposed by Georgi and Machecek~\cite{Georgi:1985nv}.
In the Georgi Machacek (GM) model, the Higgs sector is extended by a real 
triplet with $Y=0$ and 
a complex triplet with $Y=2$ in addition to the usual SM doublet ($Y =1$). 
After EWSB, this leads to a rich Higgs sector with intriguing phenomenology.
The Higgs sector of the GM has ten physical states that are organized based
on their transformation properties under the approximate global \SUtwo symmetry
of the scalar fields, referred two as custodial symmetry. There are two singlets,
one of which is associated with the observed Higgs boson, a triplet, and 
a fiveplet ($\H_5^{++}$,$\H_5^{+}$,$\H_5^{0}$,$\H_5^{-}$,$\H_5^{--}$) that
is fermiophobic. If the mass of the triplet states is greater than the
mass of the fiveplet, the only production mechanism for $\PH^{\pm}$ at the LHC
is vector boson fusion. The production cross section is proportional to the variable
$\s_{\PH}^2 \equiv \sin^2{\theta_{\PH}} = $, the ratio
of the vacuum expectation values of the triplet fields. Therefore, the leptonic $\WZjj$ 
state probed in this thesis is well-suited for further probes of this model, 
which is significantly less constrained than those charged Higgs with predominantly
leptonic decays.

\subsection{Generalizing new interactions with effective field theory}

If new physics is present VBS WZ production 

\section{Previous results}
